First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
more cleaning to the parapgraph after equation 6

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of the electroproduction of 
a real photon includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target elastic form factors, which are well known in 
this kinematic region, while the DVCS amplitude depends on the GPDs. In our 
kinematics, the cross section of the real photon electroproduction is dominated 
by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
with a cross section measurement. However, the DVCS-BH interference term offers 
an easier experimental access by generating spin asymmetries. We have, in 
particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
Belitsky:2008bz} as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Explicit expressions of the kinematic factors $\alpha_i$ are derived from 
expressions in Ref.~\cite{Belitsky:2008bz}:
\begin{equation}
\begin{split}
&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi) \\
&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi) \\
&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right) \\
&\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{split}
\end{equation}
Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics in the 
leptonic tensor of the interference amplitude, while $c_{0,1,2}^{BH}$ 
are the Fourier harmonics of the BH amplitude\footnote{The explicit 
expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
propagators and only include $\cos(\phi)$ dependencies.
We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 
one can extract unambiguously both the imaginary and real parts of $\mathcal{H}_{A}$
with a fit of the $A_{LU}(\phi)$ distribution.

>>>>

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of the electroproduction of 
a real photon includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target elastic form factors, which are well known in 
this kinematic region, while the DVCS amplitude depends on the GPDs. In our 
kinematics, the cross section of the real photon electroproduction is dominated 
by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
with a cross section measurement. However, the DVCS-BH interference term offers 
an easier experimental access by generating spin asymmetries. We have, in 
particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
Belitsky:2008bz} as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Explicit expressions of the kinematic factors $\alpha_i$ are derived from 
expressions in Ref.~\cite{Belitsky:2008bz}:
\begin{equation}
\begin{split}
&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi) \\
&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi) \\
&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right) \\
&\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{split}
\end{equation}
Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
interference amplitude in the leptonic tensor, while $c_{0,1,2}^{BH}$ 
are the Fourier harmonics of the BH amplitude\footnote{The explicit 
expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
propagators and only include $\cos(\phi)$ dependencies.
We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 
one can extract unambiguously both the imaginary and real parts of $\mathcal{H}_{A}$
with a fit of the $A_{LU}(\phi)$ distribution.
